A molecular dynamics study of the solvation of carbon dioxide in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2018-09-08 ionic_liquids.tex
Changes in Table 1

As will be shown below, the prediction of activity coefficients requires additional simulations of the solute as a pure liquid phase, whose properties we denote here by a superscript ``$0$''.
We start by using a standard thermodynamic relation \cite{Tester} to write the solute activity coefficient $\gamma_s$ in terms of chemical potentials as
\begin{equation}
\label{eq:gamma}
\ln \gamma_s = \frac{\mu_s^l - \mu_s^{l,0}}{k_B T} - \ln x_s,
\end{equation}

@@

\begin{table*}
\begin{threeparttable}
\caption{Comparison of predicted and experimental densities for differents models of \ce{[emim][B(CN)_4]} via NPT-MD simulations at $T = 298.0~\text{K}$ and $P = 1.0~\text{atm}$. The experimental density is $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
\begin{tabular}{ c  c  c  c  c}  
\hline \hline
\ce{[emim][B(CN)_4]}&  $\rho_\text{sim}$ & error (\%)\tnote{a}  & $\rho_\text{sim}$ & error (\%)\tnote{a} \\
model & (g/cm$^{3}$) &  &  (g/cm$^{3}$) &  \\
			\hline
& \multicolumn{2}{c}{Flexible ions/Ewald method} & \multicolumn{2}{c}{Rigid ions/DSF method} \\
Koller y col. \cite{Koller_2012}    & 1.046 & 1.0 & 1.038 & 0.2 \\
Batista y col. \cite{Batista_2015}  & 0.989 & 4.6 & 0.988 & 4.7 \\
Liu y col. \cite{Liu_2014}          & 1.001 & 3.4 & 0.991 & 4.4 \\
Weber y Kirchner. \cite{Weber_2016} & 1.015 & 2.1 & 1.022 & 1.4  \\
 \hline \hline
\label{table:props_dsf} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$($\rho^{\text{exp}}$$ - $$\rho^\text{sim}$)/$\rho^{\text{exp}}$.
\end{tablenotes}
\end{threeparttable}
\end{table*}

>>>>

As will be shown below, the prediction of activity coefficients requires additional simulations of the solute as a pure liquid phase, whose properties we denote here by a superscript ``$0$''.
We start by using a standard thermodynamic relation \cite{Tester} to write the solute activity coefficient $\gamma_s$ in terms of chemical potentials as
\begin{equation}
\label{eq:gamma}
\ln \gamma_s = \frac{\mu_s^l - \mu_s^{l,0}}{k_b T} - \ln x_s,
\end{equation}

@@

\begin{table*}
\centering
\caption{Comparison of predicted and experimental densities for different models of \ce{[emim][B(CN)_4]} via NPT-MD simulations at $T = 298.0~\text{K}$ and $P = 1.0~\text{atm}$. The experimental density is $1.036~\mathrm{g/cm^3}$ \cite{Doma_ska_2011}.}
\begin{tabular}{ccccc}
\hline
\hline
\ce{[emim][B(CN)_4]} model                        & 
\multicolumn{2}{c}{Flexible ions \& Ewald method} &
\multicolumn{2}{c}{Rigid ions \& DSF method}      \\
                                            &
$\rho_\text{sim}$ (g/cm\textsuperscript{3}) &
error (\%)                                  &
$\rho_\text{sim}$ (g/cm\textsuperscript{3}) &
error (\%)                                  \\
\hline
Koller \textit{et al}. \cite{Koller_2012}    & 1.046 & 1.0 & 1.038 & 0.2 \\
Batista \textit{et al}. \cite{Batista_2015}  & 0.989 & 4.6 & 0.988 & 4.7 \\
Liu \textit{et al}. \cite{Liu_2014}          & 1.001 & 3.4 & 0.991 & 4.4 \\
Weber and Kirchner \cite{Weber_2016}         & 1.015 & 2.1 & 1.022 & 1.4  \\
\hline
\hline
\label{table:props_dsf}
\end{tabular}
\end{table*}
